Omics-based Single Step Trait Prediction

### 2017-03-24 paper/manuscript.tex
Init results on inbred lines

\section*{Results}
\Genetics2level{Inbred lines}

% latex table generated in R 3.3.3 by xtable 1.8-2 package
% Wed Mar 22 08:40:11 2017
% Script: ./analysis/maizego_core_fraction_plot_predictive_abilities.R
\begin{table}[ht]
\label{tbl:InbredTable}
\centering
\caption{Predictive abilities and corresponding coefficients of variation for different core sets from the tropical/subtropical material of the maize diversity panel. As predictors, genomic (G) data, transcriptomic (T) data and their combination (GT) were used. The decimal after the predictor name indicates the size of the genetic material that was covered by inbred lines in the core set.} 
\begin{tabular}{rllllll}
  \toprule
 & 100grainweight & cobweight & Eardiameter & Kernelwidth & Plantheight & Silkingtime \\ 
  \midrule
\multicolumn{6}{l}{{\bfseries Only incomplete predictor: FALSE}}\\
G\_Full & 0.43 (0.0733) & 0.37 (0.1734) & 0.39 (0.0535) & 0.34 (0.0455) & 0.45 (0.0755) & 0.53 (0.0297) \\ 
  GT\_Full & 0.44 (0.0748) & 0.33 (0.1727) & 0.4 (0.0543) & 0.34 (0.0425) & 0.4 (0.0707) & 0.53 (0.0285) \\ 
   \midrule
\multicolumn{6}{l}{{\bfseries Only incomplete predictor: TRUE}}\\
G\_1.0 & 0.36 (0.0773) & 0.21 (0.1678) & 0.3 (0.0527) & 0.34 (0.0472) & 0.41 (0.078) & 0.45 (0.0302) \\ 
  T\_1.0 & 0.4 (0.0747) & 0.15 (0.1568) & 0.37 (0.0509) & 0.36 (0.0423) & 0.32 (0.0692) & 0.49 (0.0279) \\ 
  GT\_0.9 & 0.39 (0.0792) & 0.21 (0.1692) & 0.38 (0.0561) & 0.41 (0.0459) & 0.29 (0.075) & 0.49 (0.0311) \\ 
  GT\_0.8 & 0.4 (0.0774) & 0.21 (0.1581) & 0.36 (0.0515) & 0.41 (0.0458) & 0.29 (0.0737) & 0.49 (0.0288) \\ 
  GT\_0.7 & 0.37 (0.0734) & 0.1 (0.1555) & 0.31 (0.0508) & 0.37 (0.0422) & 0.33 (0.0755) & 0.52 (0.028) \\ 
  GT\_0.6 & 0.4 (0.0739) & 0.13 (0.1563) & 0.27 (0.0497) & 0.37 (0.0417) & 0.42 (0.075) & 0.55 (0.0272) \\ 
  GT\_0.5 & 0.41 (0.0671) & 0.16 (0.1549) & 0.31 (0.0486) & 0.4 (0.0414) & 0.44 (0.0748) & 0.49 (0.0278) \\ 
  GT\_0.4 & 0.39 (0.0697) & 0.2 (0.1558) & 0.33 (0.0486) & 0.35 (0.0428) & 0.38 (0.0727) & 0.52 (0.028) \\ 
  GT\_0.3 & 0.36 (0.0711) & 0.2 (0.1566) & 0.28 (0.0503) & 0.37 (0.044) & 0.42 (0.0736) & 0.5 (0.028) \\ 
  GT\_0.2 & 0.35 (0.072) & 0.23 (0.1645) & 0.26 (0.0519) & 0.36 (0.0474) & 0.38 (0.0722) & 0.44 (0.0273) \\ 
  GT\_0.1 & 0.29 (0.0762) & 0.21 (0.1659) & 0.23 (0.0522) & 0.32 (0.0471) & 0.4 (0.0743) & 0.39 (0.0302) \\ 
   \bottomrule
\multicolumn{6}{l}{}\\
\end{tabular}
\end{table}

@@

% latex table generated in R 3.3.3 by xtable 1.8-2 package
% Thu Mar 16 08:16:30 2017
% Script: ./analysis/uhoh_plot_predictive_abilities.R
\begin{table}[ht]
\label{tbl:HybridTable}
\centering
\caption{Predictive abilities and corresponding coefficients of variation for the set of maize hybrids. As predictors, pedigree (P), genomic (G), transcriptomic (T) data and combinations thereof we used.} 
\begin{tabular}{rllllll}
  \toprule
 & DMY & DMC & FAT & PRO & STA & SUG \\ 
  \midrule
\multicolumn{6}{l}{{\bfseries Only incomplete predictor: FALSE}}\\
P & 0.54 (0.049) & 0.48 (0.052) & 0.21 (0.037) & 0.6 (0.019) & 0.35 (0.043) & 0.42 (0.117) \\ 
  G & 0.74 (0.052) & 0.63 (0.052) & 0.43 (0.036) & 0.65 (0.022) & 0.46 (0.046) & 0.47 (0.126) \\ 
  PG & 0.71 (0.054) & 0.57 (0.055) & 0.35 (0.038) & 0.62 (0.023) & 0.39 (0.048) & 0.42 (0.13) \\ 
  PT & 0.73 (0.056) & 0.53 (0.059) & 0.35 (0.04) & 0.61 (0.025) & 0.31 (0.05) & 0.37 (0.14) \\ 
  GT & 0.75 (0.053) & 0.61 (0.055) & 0.43 (0.037) & 0.65 (0.024) & 0.44 (0.048) & 0.44 (0.134) \\ 
   \midrule
\multicolumn{6}{l}{{\bfseries Only incomplete predictor: TRUE}}\\
T & 0.75 (0.055) & 0.34 (0.062) & 0.4 (0.041) & 0.47 (0.029) & 0.16 (0.05) & 0.27 (0.145) \\ 
  P & 0.46 (0.047) & 0.53 (0.05) & 0.23 (0.037) & 0.46 (0.023) & 0.38 (0.039) & 0.34 (0.132) \\ 
  G & 0.67 (0.053) & 0.47 (0.055) & 0.43 (0.038) & 0.48 (0.027) & 0.36 (0.046) & 0.35 (0.132) \\ 
   \bottomrule
\multicolumn{6}{l}{}\\
\end{tabular}
\end{table}

>>>>

\section*{Results}
\Genetics2level{Inbred lines}
At the level of the 149 genotypes for which both, genomic (G) and 
transcriptomic (T) information, were available, the use of T yielded higher
predictive abilities than the use of G for four out of six traits
\ref{table:InbredTable}.
In terms of predictive ability, the absolute advantage of T over G was as large 
as 0.04 as observed for the traits '100grainweight', 'Eardiameter' and 
'Silkingtime'.
Except for 'Kernelwidth', the predictive ability for predictions based on
G and the full set of inbred lines ($n = 211$) was always higher than for the 
reduced set of inbred lines ($n = 149$).
The combination of G and T (\textit{i.e.}, GT) in a single-step approach for the 
prediction of all 211 lines performed at least as well as G alone when T was 
superior over G for the reduced set of 149 lines.
In the case of '100grainweight' and 'Eardiameter', the use of GT yielded a 
slight improvement in predictive ability over G.
Where T was a worse predictor for the reduced set of 149 lines than G,
predictive abilities of GT for the full set of 211 lines were also worse than 
those based on G alone.

% latex table generated in R 3.3.3 by xtable 1.8-2 package
% Fri Mar 24 11:34:47 2017
% Script: ./analysis/maizego_core_fraction_plot_predictive_abilities.R
\begin{table}[ht]
\label{table:InbredTable}
\centering
\caption{Predictive abilities and corresponding coefficients of variation for different core sets from the tropical/subtropical material of the maize diversity panel. As predictors, genomic (G) data, transcriptomic (T) data and their combination (GT) were used. The decimal after the predictor name indicates the size of the genetic material that was covered by inbred lines in the core set.} 
\begin{tabular}{rllllll}
  \toprule
 & 100grainweight & cobweight & Eardiameter & Kernelwidth & Plantheight & Silkingtime \\ 
  \midrule
\multicolumn{6}{l}{{\bfseries Only incomplete predictor: FALSE}}\\
G Full & 0.43 (0.073) & 0.37 (0.173) & 0.39 (0.053) & 0.34 (0.045) & 0.45 (0.076) & 0.53 (0.03) \\ 
  GT Full & 0.44 (0.075) & 0.33 (0.173) & 0.4 (0.054) & 0.34 (0.043) & 0.4 (0.071) & 0.53 (0.028) \\ 
   \midrule
\multicolumn{6}{l}{{\bfseries Only incomplete predictor: TRUE}}\\
G 1.0 & 0.36 (0.077) & 0.21 (0.168) & 0.3 (0.053) & 0.34 (0.047) & 0.41 (0.078) & 0.45 (0.03) \\ 
  T 1.0 & 0.4 (0.075) & 0.15 (0.157) & 0.37 (0.051) & 0.36 (0.042) & 0.32 (0.069) & 0.49 (0.028) \\ 
  GT 0.1 & 0.29 (0.076) & 0.21 (0.166) & 0.23 (0.052) & 0.32 (0.047) & 0.4 (0.074) & 0.39 (0.03) \\ 
  GT 0.2 & 0.35 (0.072) & 0.23 (0.164) & 0.26 (0.052) & 0.36 (0.047) & 0.38 (0.072) & 0.44 (0.027) \\ 
  GT 0.3 & 0.36 (0.071) & 0.2 (0.157) & 0.28 (0.05) & 0.37 (0.044) & 0.42 (0.074) & 0.5 (0.028) \\ 
  GT 0.4 & 0.39 (0.07) & 0.2 (0.156) & 0.33 (0.049) & 0.35 (0.043) & 0.38 (0.073) & 0.52 (0.028) \\ 
  GT 0.5 & 0.41 (0.067) & 0.16 (0.155) & 0.31 (0.049) & 0.4 (0.041) & 0.44 (0.075) & 0.49 (0.028) \\ 
  GT 0.6 & 0.4 (0.074) & 0.13 (0.156) & 0.27 (0.05) & 0.37 (0.042) & 0.42 (0.075) & 0.55 (0.027) \\ 
  GT 0.7 & 0.37 (0.073) & 0.1 (0.156) & 0.31 (0.051) & 0.37 (0.042) & 0.33 (0.075) & 0.52 (0.028) \\ 
  GT 0.8 & 0.4 (0.077) & 0.21 (0.158) & 0.36 (0.051) & 0.41 (0.046) & 0.29 (0.074) & 0.49 (0.029) \\ 
  GT 0.9 & 0.39 (0.079) & 0.21 (0.169) & 0.38 (0.056) & 0.41 (0.046) & 0.29 (0.075) & 0.49 (0.031) \\ 
  GT A1 & 0.32 (0.079) & 0.03 (0.155) & 0.28 (0.053) & 0.32 (0.045) & 0.31 (0.073) & 0.46 (0.03) \\ 
  GT A2 & 0.4 (0.081) & 0.18 (0.164) & 0.32 (0.055) & 0.33 (0.046) & 0.36 (0.073) & 0.47 (0.03) \\ 
  GT A3 & 0.3 (0.071) & 0.1 (0.164) & 0.34 (0.054) & 0.41 (0.041) & 0.33 (0.072) & 0.41 (0.029) \\ 
   \bottomrule
\multicolumn{6}{l}{}\\
\end{tabular}
\end{table}

@@

% latex table generated in R 3.3.3 by xtable 1.8-2 package
% Thu Mar 16 08:16:30 2017
% Script: ./analysis/uhoh_plot_predictive_abilities.R
\begin{table}[ht]
\label{table:HybridTable}
\centering
\caption{Predictive abilities and corresponding coefficients of variation for the set of maize hybrids. As predictors, pedigree (P), genomic (G), transcriptomic (T) data and combinations thereof we used.} 
\begin{tabular}{rllllll}
  \toprule
 & DMY & DMC & FAT & PRO & STA & SUG \\ 
  \midrule
\multicolumn{6}{l}{{\bfseries Only incomplete predictor: FALSE}}\\
P & 0.54 (0.049) & 0.48 (0.052) & 0.21 (0.037) & 0.6 (0.019) & 0.35 (0.043) & 0.42 (0.117) \\ 
  G & 0.74 (0.052) & 0.63 (0.052) & 0.43 (0.036) & 0.65 (0.022) & 0.46 (0.046) & 0.47 (0.126) \\ 
  PG & 0.71 (0.054) & 0.57 (0.055) & 0.35 (0.038) & 0.62 (0.023) & 0.39 (0.048) & 0.42 (0.13) \\ 
  PT & 0.73 (0.056) & 0.53 (0.059) & 0.35 (0.04) & 0.61 (0.025) & 0.31 (0.05) & 0.37 (0.14) \\ 
  GT & 0.75 (0.053) & 0.61 (0.055) & 0.43 (0.037) & 0.65 (0.024) & 0.44 (0.048) & 0.44 (0.134) \\ 
   \midrule
\multicolumn{6}{l}{{\bfseries Only incomplete predictor: TRUE}}\\
T & 0.75 (0.055) & 0.34 (0.062) & 0.4 (0.041) & 0.47 (0.029) & 0.16 (0.05) & 0.27 (0.145) \\ 
  P & 0.46 (0.047) & 0.53 (0.05) & 0.23 (0.037) & 0.46 (0.023) & 0.38 (0.039) & 0.34 (0.132) \\ 
  G & 0.67 (0.053) & 0.47 (0.055) & 0.43 (0.038) & 0.48 (0.027) & 0.36 (0.046) & 0.35 (0.132) \\ 
   \bottomrule
\multicolumn{6}{l}{}\\
\end{tabular}
\end{table}
